Even-point Multi-loop Unitarity and its Applications: Exponentiation, Anomalies and Evanescence

### 2023-07-05 eventPointTwoLoop.tex
not much

In ref. \cite{Elvang:2020kuj}, the authors identified a candidate 4D counterterm that cancels this anomalous matrix element, which we have called $\mathcal{T}^{\text{4D}}_{(++++)}$, thereby restoring duality invariance through one-loop. As noted in the previous section, the one-loop matrix element can be mapped to our $D$-dimensional operator basis. In general, all available 4D tensor structures at $\mathcal{O}(\alpha'^4)$ map onto our $D$-dimensional basis. One particular map we provide below

>>>>

In ref. \cite{Elvang:2020kuj}, the authors identified a candidate 4D counterterm that cancels this anomalous matrix element, whose prediction we have called $\mathcal{T}^{\text{4D}}_{(++++)}$, thereby restoring duality invariance through one-loop. As noted in the previous section, the one-loop matrix element can be mapped to our $D$-dimensional operator basis. In general, all available 4D tensor structures at $\mathcal{O}(\alpha'^4)$ map onto our $D$-dimensional basis. One particular map we provide below
